---
title: "Homework 6"
author: "Hongji Jiang"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 2

## Import and tidy up the dataset
```{r}
homicide_data = read_csv("./data/homicide-data.csv")
```
This dataset has `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns. The columns(variables) are `r names(homicide_data)` and each row is a homicide incident.
```{r}
homicide_data=
  homicide_data %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    solved = ifelse(disposition == "Closed by arrest", 1, 0),
    victim_age = as.numeric(victim_age)
    ) %>%
    filter(city_state != "Dallas, Tx", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL") %>% 
  filter(victim_race %in% c("Black", "White")) %>% 
  drop_na(victim_age)
```
Created a new variable `city_state` by concatenating city and state, seperateing with ','.
```{r}
logistic_Baltimore = 
  homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) 
```

```{r}
logistic_Baltimore %>% 
  broom::glance()
```

```{r}
logistic_Baltimore %>% 
  broom::tidy() %>%
  mutate(OR = exp(estimate)) %>%
  mutate(
    lower_ci = exp(estimate-1.96*std.error),
    upper_ci = exp(estimate+1.96*std.error)
  ) %>% 
  filter(term == "victim_sexMale") %>%
  select(term, Log_OR = estimate, OR, lower_ci, upper_ci) %>% 
  knitr::kable(digits = 3)
```

```{r}
logistic_all_cities = function(dataset) {
    dataset %>%
    glm(solved ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
    broom::tidy() %>% 
    mutate(
      OR = exp(estimate),
      lower_ci = exp(estimate - 1.96 * std.error),
      upper_ci = exp(estimate + 1.96 * std.error)) %>%
  filter(term == "victim_sexMale") %>%
  select(term, Log_OR = estimate, OR, lower_ci, upper_ci)
}
```
Create a function to be applied to the dataset in the next steps for each of the cities.
```{r}
logit_result_cities = 
  homicide_data %>% 
  nest(df = -city_state) %>% 
  mutate(
    result = map(df, logistic_all_cities)
  ) %>% 
  unnest(result) %>% 
  select(-df) 
```

```{r}

logit_result_cities %>% 
  knitr::kable(digits = 3)
```


# Question 3 
```{r}
birthweight_data = 
  read_csv("./data/birthweight.csv") %>% 
    mutate(
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace),
    babysex = as.factor(babysex)
    ) %>%
  drop_na()
```

```{r}
proposed_model = lm(bwt ~ fincome+blength+gaweeks, data = birthweight_data)
```

```{r}
proposed_model %>%
  broom::tidy() %>% 
  knitr::kable(digits = 4)
```

```{r}
proposed_plot =
  birthweight_data %>% 
  modelr::add_residuals(proposed_model) %>%
  modelr::add_predictions(proposed_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5, cex=0.3) +
  labs(
    title = "Residuals vs. Fitted values",
    x = "fitted_values",
    y = "residuals")
proposed_plot
```


